Qualifying Exam\phantom{:} \,\normalsize Physics 2020 @ YMSC, Tsinghua

### 2021-05-09 Strings2020/strings1/strings1.tex
Add minor tweaks to various notes

	Notice that we have obtained a conserved current using a generic $
		\var{z}
		= \epsilon(z,\bar{z}),
		\var{\bar{z}}
		= \bar{\epsilon}(z,\bar{z})
	$; by setting $\epsilon = \epsilon(z)$, we get \textit{a} energy momentum tensor\footnote{
		Note that the energy momentum tensor obtained in this way is generally \textit{not} unique: it can be off by a boundary term; see Luboš' comment at \https{physics.stackexchange.com/a/96100}, also \arxiv{1601.03616}. However, it is possible to fix this redundancy by considering $Tb$ OPE and match its conformal dimension. I would like to thank \textit{林般} for pointing this out. 
	}:
	\begin{equation}
		T(z)
		= \normorder{(\pd b)\,c}
			- \lambda\,\pd(\normorder{bc})
	\end{equation}
	Normal ordering is added manually to remove singular terms.

>>>>

	Notice that we have obtained a conserved current using a generic $
		\var{z}
		= \epsilon(z,\bar{z}),
		\var{\bar{z}}
		= \bar{\epsilon}(z,\bar{z})
	$; by setting $\epsilon = \epsilon(z)$, we get \textit{a} energy momentum tensor\footnote{
		Note that the energy momentum tensor obtained in this way is generally \textit{not} unique: it can be off by a boundary term or any term that vanish on-shell; see Luboš' comment at \https{physics.stackexchange.com/a/96100}, also \arxiv{1601.03616}. However, it is possible to fix this redundancy by considering $Tb$ OPE and match its conformal dimension. I would like to thank \textit{林般} for pointing this out. 
	}:
	\begin{equation}
		T(z)
		= \normorder{(\pd b)\,c}
			- \lambda\,\pd(\normorder{bc})
	\end{equation}
	Normal ordering is added manually to remove singular terms.

### 2021-05-09 alpha/Exam/exam.tex
Add minor tweaks to various notes

	\item At 1-loop $\order{\lambda}$, if we do not include counterterm contributions, then there is only one diagram contributing to $M(p^2)$:
	\begin{equation}
	%% ref: <https://tex.stackexchange.com/q/387810/193356>
		\raisebox{-.2\height}{
			\feynmandiagram[
				scale=.7
				,small
				,layered layout
				,horizontal=a to b
			]{
				a -- b [dot]
				-- [out=135, in=45, loop
					,min distance=3.5\baselineskip
					] b
				-- c
			};
		}
		= (-i\lambda)\cdot\frac{1}{2}
			\int \frac{\dd[D]{k}}{(2\pi)^D}
				\frac{-i}{k^2 + m^2 - i\epsilon}
	\end{equation}
	Here $\frac{1}{2}$ is the symmetry factor of the diagram; alternative, we can count the distinct ways of connection the 4 legs of the $\phi^4$ vertex and divide it by $4!$, which is indeed $
		\frac{4\times 3}{4!} = \frac{1}{2}
	$.

>>>>

	\item At 1-loop $\order{\lambda}$, if we do not include counterterm contributions, then there is only one diagram contributing to $M(p^2)$:
	\begin{equation}
	%% ref: <https://tex.stackexchange.com/q/387810/193356>
		\raisebox{-.2\height}{
			\feynmandiagram[
				scale=.7
				,small
				,layered layout
				,horizontal=a to b
			]{
				a -- b [dot]
				-- [out=135, in=45, loop
					,min distance=3.5\baselineskip
					] b
				-- c
			};
		}
		= (-i\lambda)\cdot\frac{1}{2}
			\int \frac{\dd[D]{k}}{(2\pi)^D}
				\frac{-i}{k^2 + m^2 - i\epsilon}
	\end{equation}
	Here $\frac{1}{2}$ is the symmetry factor of the diagram; alternative, we can count the distinct ways of connecting the 4 legs of the $\phi^4$ vertex and divide it by $4!$, which is indeed $
		\frac{4\times 3}{4!} = \frac{1}{2}
	$.
